---
title: "Data Analytic with TATA"
subtitle: "by RStudio"
author: "Pakakorn Kaeoluan"
date: "2023/7/4"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
    theme: sandstone
    highlight: kate
  pdf_document: 
    latex_engine: xelatex
    toc: yes
    toc_depth: '3'
  word_document: default
---


```{r, echo=FALSE,warning=FALSE}

library(tidyverse)
library(rvest)
library(readxl)
library(dplyr)
```

# **1.Import Data**
```{r, echo=FALSE,warning=FALSE}
df<-read_excel("OnlineRetail.xlsx")
df%>%
  tibble()
```

# **2.Data prep**
```{r, echo=FALSE,warning=FALSE}
## check NA
df$InvoiceNo%>%
  mean()
## summary
df%>%
  summary()
## substitue quantitative data  with median
df$Quantity<-ifelse(df$Quantity<0,
                    median(df$Quantity,na.rm = TRUE),
                    df$Quantity)

df$UnitPrice<-ifelse(df$UnitPrice<=0,
                    median(df$UnitPrice,na.rm = TRUE),
                    df$UnitPrice)
## delete NA value
dfclean<-df%>%
  na.omit()
```

# **3.Analysis: Present to CMO**  
## 3.1 CMO: Which item is the most sales in the UK?
```{r,echo=FALSE,warning=FALSE}
dfclean%>%
  filter(Country=="United Kingdom")%>%
  group_by(Description)%>%
  summarise(sum=sum(Quantity))%>%
  arrange(desc(sum))
```
- ANS: PAPER CRAFT , LITTLE BIRDIE  has the best seller in UK

## 3.2 CMO: Give me 5 items of the worst sales on Dec,2010?
```{r,echo=FALSE,warning=FALSE}
dfclean$InvoiceDate<-as.Date(dfclean$InvoiceDate)
dfclean%>%
  filter(months(InvoiceDate)=="十二月" & InvoiceDate <= '2010-12-31')%>%
  group_by(Description)%>%
  summarise(sum=sum(Quantity))%>%
  arrange(sum)%>%
  head(n=5)
```
- ANS: 
  1. 3D HEARTS  HONEYCOMB PAPER GARLAND   
  2. 5 STRAND GLASS NECKLACE AMBER         
  3. 75 GREEN FAIRY CAKE CASES             
  4. AMBER DROP EARRINGS W LONG BEADS      
  5. AMBER FINE BEAD NECKLACE W TASSEL 
  
## 3.3 CMO: How many transactions of PAPER CRAFT?
```{r,echo=FALSE,warning=FALSE}
dfclean%>%
  select(StockCode,Description,Quantity,InvoiceDate,Country,InvoiceNo)%>%
  filter(grepl("PAPER CRAFT",Description))
```
- ANS: 2 transactions

## 3.4 CMO: Please show me line chart of Total Sales in 2011
```{r,echo=FALSE,warning=FALSE}
dfclean_viz1<-dfclean%>%
  filter(InvoiceDate>'2010-12-31'&InvoiceDate<'2012-01-01')
  
dfclean_viz1$InvoiceDate<-months(dfclean_viz1$InvoiceDate)

dfclean_viz1<-dfclean_viz1%>%
  rename(month=InvoiceDate)

dfclean_viz1<-dfclean_viz1%>%
  group_by(month)%>%
  summarise(sum(Quantity))

dfclean_viz1<-dfclean_viz1%>%
  rename(Qty=`sum(Quantity)`)
  
dfclean_viz1%>%
  ggplot(aes(month,Qty))+
  geom_col()+
  theme_bw()+
  labs(x="Month",y="Total Sales",title = "Total sales in 2011")
```

# **4.Analysis: Present to CEO**  
## 4.1 CEO: Which month has the most revenue in 2011
```{r,echo=FALSE,warning=FALSE}
# first we add revenue column by multiply between quantity and unit price
dfclean<-dfclean%>%
  mutate(revenue=Quantity*UnitPrice)
# then seek an answer
dfclean%>%
  filter(InvoiceDate>'2010-12-31')%>%
  group_by(months(InvoiceDate))%>%
  summarise(Total_revenue=sum(revenue))%>%
  rename(month=`months(InvoiceDate)`)%>%
  arrange(Total_revenue)
```
- ANS: December has the most revenue in 2011


## 4.2 CEO: Which quarter has the fewest revenue in 2011
```{r,echo=FALSE,warning=FALSE}
# first add the quarter in the column
dfclean<-dfclean%>%
  mutate(Quarter=quarters.POSIXt(InvoiceDate))
# then seek an answer
dfclean%>%
  filter(InvoiceDate>'2010-12-31')%>%
  group_by(Quarter)%>%
  summarise(Total_revenue=sum(revenue))%>%
  arrange(Total_revenue)
```
- ANS: Q1 has the fewest revenue in 2011


## 4.3 CEO: Which country is the best choice to expand project
```{r,echo=FALSE,warning=FALSE}
dfclean%>%
  group_by(Country)%>%
  summarise(Total_revenue=sum(revenue))%>%
  arrange(Total_revenue)
```
- ANS: UAE has the most revenue country. So we might plan to expand project in there.


## 4.4 CEO: Describe revenue in each country and month by visualization in UK and UAE
```{r,echo=FALSE,warning=FALSE}
dfclean_viz2<-dfclean%>%
  filter(InvoiceDate>'2010-12-31')%>%
  mutate(month=months(InvoiceDate))
  
  
dfclean_viz2<-dfclean_viz2%>%
  group_by(Country,month)%>%
  summarise(sum(revenue))


dfclean_viz2%>%
  filter(!Country %in% c('United Kingdom','Unspecified','United Arab Emirates'))%>%
  ggplot(aes(Country,`sum(revenue)`,fill=month))+
  geom_col()+
  theme_bw()+
  labs(x="Country",y="Total Revenue",title = "Total Revenue in 2011")
```

  